---
title: "Plotly Demo"
author: "Tony Wen"
date: "4/13/2022"
output: html_document
---

##### package deposit
```{r}
library(tidyverse); library(ggplot2)

library(plotly); library(shiny)
```

## `ggplotly()`
### `BeerPrice.csv` Demo

```{r}
BP = read.csv("https://raw.githubusercontent.com/nazzstat/DataVisualization/master/BeerPrices.csv")
```

+ baseline ggplot
```{r}
ggplot(BP)+
  geom_point(aes(x = Year, y = Price.per.Ounce))
```

+ wrap baseline plot in `ggplotly()`
```{r}
ggplotly(
  
  ggplot(BP)+
  geom_point(aes(x = Year, y = Price.per.Ounce))
  
)
```

+ customize popup labels
```{r}
ggplotly(
  
  ggplot(BP)+
  geom_point(aes(x = Year, y = Price.per.Ounce,
                 text = paste("Team:", Team,
                              "<br>City:", City))),
  
  # dictate what shows up in the pop up
  tooltip = "text"
  
)
```

+ Create Interactive Elements Based on Plotly Hover in Shiny
```{r}
ui = fluidPage(
  plotlyOutput("plotly"),
  tableOutput("HoverTable")
)

server = function(input, output){
  
  output$plotly = renderPlotly(
    {
      ggplotly(
        ggplot(BP)+
          geom_point(aes(x = Year, y = Price.per.Ounce,
                         text = paste("Team:", Team,
                                      "<br>City:", City,
                                      "<br>Price per Beer:", Price))),
        tooltip = "text",
        source = "main"
      )
    }
  )
  
  output$HoverTable = renderTable(
    {
      eventdat = event_data("plotly_hover", source = "main")
      
      # default with no hover 
      if(is.null(eventdat) == T) return (NULL)
      
      # store the hover coordinates
      x = as.numeric(eventdat[["x"]])
      y = as.numeric(eventdat[["y"]])
      
      # use the coordinates for filtering
      BP %>%
        filter(Price.per.Ounce == y, Year == x)
      
    }
  )
  
}


shinyApp(ui, server)
```


### `Spotify` Demo
```{r}
oneD = read.csv("https://raw.githubusercontent.com/nazzstat/DataVisualization/master/one_direction.csv",stringsAsFactors=FALSE)
```

```{r}
glimpse(oneD)
```

+
```{r}
ggplotly(
  ggplot(oneD)+
    geom_point(aes(x = tempo, y = danceability, color = popularity,
                   text = paste("Title:", name,
                                "<br>Artist:", artists,
                                "<br> Year:", year,
                                "<br>Popularity:", popularity)))+
    geom_smooth(aes(x = tempo, y = danceability), se = F, color = "black", lwd = 0.5)+
    scale_color_distiller("popularity", palette = "RdPu", direction = 1),
  tooltip = "text"
)
```

+ Construct a shiny with ploty that display annual song popularity
```{r eval = F}
ui = fluidPage(
  plotlyOutput("mainplot"),
  textOutput("test"),
  plotOutput("AnnualRank")
)

server = function(input, output){
  
  output$mainplot = renderPlotly(
    {
      ggplotly(
        ggplot(oneD)+
          geom_point(aes(x = tempo, y = danceability, color = popularity,
                         text = paste("Title:", name,
                                      "<br>Artist:", artists,
                                      "<br> Year:", year,
                                      "<br>Popularity:", popularity)))+
          geom_smooth(aes(x = tempo, y = danceability), 
                      se = F, color = "black", lwd = 0.5)+
          scale_color_distiller("popularity", palette = "RdPu",
                                direction = 1),
        tooltip = "text",
        source = "main"
      )
    }
  )
  output$AnnualRank = renderPlot({
    event_dat = event_data("plotly_hover", source = "main")
    
    # default
    if(is.null(event_dat) == T) return(NULL)
    
    
    
    oneD %>% 
      filter(danceability == as.numeric(event_dat[['y']]),
             tempo == as.numeric(event_dat[['x']])) %>%
      pull(year) -> YoI
    
    oneD %>% 
      filter(year == YoI) %>% 
      select(name, popularity) %>%
      arrange(desc(popularity)) %>%
      
    
    }
  })
}

shinyApp(ui, server)
```

***
***

## `plot_ly()`
+ plot directly in plotly w. slightly different syntax
+ Plot types specified by `type`:
  + "box"
  + "bar"
  + "scatter"
  <br> specify `mode = lines` for line graph
  <br> specify `mode = markers` for scatterplot
  + "scatter3d"
  + for Matrix Data
    + "heatmap"
    + "surface"

#### Demo
```{r}
plot_ly(txhousing,
        x = ~listings,
        y = ~volume,
        z = ~year,
        color = ~median,
        size = ~median,
        type = "scatter3d", # type = c("box", "bar", "heatmap", "surface")
        mode = "markers",
        text = ~city,
        hoverinfo = "text")
```


```{r}
txhousing %>% head()
```

